Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Paris version \YellowPaperVersionNumber}}

### 2024-02-20 Paper.tex
add tx type 2 (#898)
fix: typo

Here, we assume all components are interpreted by the RLP as integer values, with the exception of the access list $T_{\mathbf{A}}$ and the arbitrary length byte arrays $T_{\mathbf{i}}$ and $T_{\mathbf{d}}$.
\begin{equation}
\begin{array}[t]{lclclc}
T_{\mathrm{x}} \in \{0, 1\} & \wedge & T_{\mathrm{c}} = \beta & \wedge & T_{\mathrm{n}} \in \mathbb{N}_{256} & \wedge \\
T_{\mathrm{p}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{g}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{v}} \in \mathbb{N}_{256} & \wedge \\
T_{\mathrm{w}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{r}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{s}} \in \mathbb{N}_{256} & \wedge \\
T_{\mathrm{y}} \in \mathbb{N}_{1} & \wedge & T_{\mathbf{d}} \in \mathbb{B} & \wedge & T_{\mathbf{i}} \in \mathbb{B} & \wedge \\
T_{\mathrm{m}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{f}} \in \mathbb{N}_{256}
\end{array}
\end{equation}
where
\begin{equation}
\mathbb{N}_{\mathrm{n}} = \{ P: P \in \mathbb{N} \wedge P < 2^n \}
\end{equation}

@@

To incentivize validators to include transactions, there is an additional fee known as a \textit{priority fee}, which is also specified as wei per unit of gas consumed. The total fee fee paid by the transactor therefore is the sum of the base fee per gas and the priority fee per gas multiplied by the total gas consumed. Ether used to satisfy the priority fee is delivered to the \textit{beneficiary} address, the address of an account typically under the control of the validator.

>>>>

Here, we assume all components are interpreted by the RLP as integer values, with the exception of the access list $T_{\mathbf{A}}$ and the arbitrary length byte arrays $T_{\mathbf{i}}$ and $T_{\mathbf{d}}$.
\begin{equation}
\begin{array}[t]{lclclc}
T_{\mathrm{x}} \in \{0, 1, 2\} & \wedge & T_{\mathrm{c}} = \beta & \wedge & T_{\mathrm{n}} \in \mathbb{N}_{256} & \wedge \\
T_{\mathrm{p}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{g}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{v}} \in \mathbb{N}_{256} & \wedge \\
T_{\mathrm{w}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{r}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{s}} \in \mathbb{N}_{256} & \wedge \\
T_{\mathrm{y}} \in \mathbb{N}_{1} & \wedge & T_{\mathbf{d}} \in \mathbb{B} & \wedge & T_{\mathbf{i}} \in \mathbb{B} & \wedge \\
T_{\mathrm{m}} \in \mathbb{N}_{256} & \wedge & T_{\mathrm{f}} \in \mathbb{N}_{256}
\end{array}
\end{equation}
where
\begin{equation}
\mathbb{N}_{\mathrm{n}} = \{ P: P \in \mathbb{N} \wedge P < 2^n \}
\end{equation}

@@

To incentivize validators to include transactions, there is an additional fee known as a \textit{priority fee}, which is also specified as wei per unit of gas consumed. The total fee paid by the transactor therefore is the sum of the base fee per gas and the priority fee per gas multiplied by the total gas consumed. Ether used to satisfy the priority fee is delivered to the \textit{beneficiary} address, the address of an account typically under the control of the validator.
